Date Exercise

### 2024-06-27 data-exercise/data-exercise.qmd
Zane is helping me

---
title: "Data Exercise"
---

@@

## Loading and Checking Data
## Import Libraries
```{r}
library(MASS)
library(synthpop)
library(tidyverse)
library(dplyr)
library(writexl)
library(ggplot2)
library(broom)
```

@@

```{r}
# Write to Excel file
write_xlsx(as.data.frame(applicant_final), "Employee_Selection_Scores.xlsx")
```

```{r}
# Histogram of situational scores
ggplot(applicant_final, aes(x = situational)) +
  geom_histogram(binwidth = 5, fill = "blue", color = "black") +
  labs(title = "Histogram of Situational Scores", x = "Situational Score", y = "Frequency")
```
```{r}
# Generalized linear model plot
ggplot(applicant_final, aes(x = situational, y = performance)) +
  geom_point() +
  geom_smooth(method = "glm", se = FALSE, color = "green") +
  labs(title = "Generalized Linear Model: Situational vs Performance", x = "Situational Score", y = "Performance Score")

@@

*******Conclusion**************************************************

>>>>

---
title: "Date Exercise"
---

@@

```{r}
library(MASS)
library(synthpop)
library(tidyverse)
library(dplyr)
library(writexl)
library(ggplot2)
```

@@

```{r}
# Write to Excel file
#write_xlsx(as.data.frame(applicant_final), "Employee_Selection_Scores.xlsx")
```

```{r}
# Histogram of situational scores
ggplot(applicant_final, aes(x = situational)) +
  geom_histogram(binwidth = 5, fill = "blue", color = "black") +
  labs(title = "Histogram of Situational Scores", x = "Situational Score", y = "Frequency")
```

```{r}
# Generalized linear model plot
ggplot(applicant_final, aes(x = situational, y = performance)) +
  geom_point() +
  geom_smooth(method = "glm", se = FALSE, color = "green") +
  labs(title = "Generalized Linear Model: Situational vs Performance", x = "Situational Score", y = "Performance Score")

@@
